On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-02 Manuscript/manuscript.tex
Included Effective Sample Size Bit in Paper, still need reference

For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$.

>>>>

For estimating the mean parameter~$\mu$, \textbf{Figure~\ref{fig:mu1}} suggests 
that all methods eventually approach correct coverage of $\mu$ as sample size 
increases. Student's $t$ CIs appear to need the smallest sample size to achieve 
correct coverage, except for samples with strong negative dependence, in which 
case, they actually over-cover $\mu$ for smaller sample sizes. For instance, for 
a sample with $n = 100$ and $\phi = -0.4$, the lower bound for a Students $t$ 
CI's coverage of $\mu$ is greater than 95\%, whereas the coverage intervals for 
other methods contain 95\%. The standard normal, percentile, BC, and BCA, and 
recentered percentile CIs require similar sample sizes to recover $\mu$ at the 
nominal level for all combinations of $n$ and $\phi$. All methods seem to 
require a smaller sample to recover $\mu$ at the nominal rate when dealing with 
negative dependence versus positive dependence. For example, BC CIs recover 
$\mu$ for $n \geq 100$ when $\phi = -0.2$, but they only recover $\mu$ for 
$n \geq 800$ when $\phi = 0.2$. In addition, as a negative dependence gets 
stronger, holding everything else equal, coverage increases, which lead to the 
Student $t$ CI's aforementioned over-coverage. As a positive dependence gets 
stronger, holding everything else equal, coverage decreases, and a larger sample 
is necessary to recover~$\mu$. A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter.

### 2024-01-02 Manuscript/reply.tex
Included Effective Sample Size Bit in Paper, still need reference

If a stationary series has a positive autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, we expect this to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter.

>>>>

We have included this comment at the end of the paragraph on estimation of 
$\mu$:

A possible explanation for this is that if a 
stationary series has a positive 
autocorrelation, the effective sample
size is decreased, whereas is a series has a negative autocorrelation, the
effective sample size is increased. Additionally, this seems to have a 
greater effect on the the estimation of the location parameter versus that
of the scale parameter or temporal dependence parameter.
